Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-27 docs/manuscript/manuscript.tex
The first body section of contribution.

%  Conclusion In the 24 SSA countries studied, an estimated 3.36 million children and 13.54 million adult females were responsible for water collection in households with collection times greater than 30 minutes. We suggest that accessibility to water, water collection by children, and gender ratios for water collection, especially when collection times are great, should be considered as key indicators for measuring progress in the water, sanitation and hygiene sector.

@@

\section{Contribution}
Lack of water accessibility is a major crisis for many vulnerable people around the world. We have determined to seek literature reviews from the past 15 years to have the most up to date information because information on water accessibility is a topic that is constantly changing throughout the world due to different international, government, and even local policies. The literature review intends to investigate different journal articles on water accessibility in a global scale. Therefore we can conduct a research to fill many major gaps  to analyze the water accessibility predictor variables which could increase and enhance water accessibility in global scale. We will always gain new insight and wisdom on information about water accessibility through the global scale as we investigate and determine literature reviews chronologically. 
\subsection{2006-2016}
Improving water accessibility have been a priority by many organizations around the world, realizing it is the basic human rights to have clean and accessible drinkable water in past 15 years. During 2006 to 2016, overall water accessibility has been improving by utilizing the indicators of the past \citep{fullerTrackingProgressGlobal2016}. However, some researchers raises concerns on lack of clarity with the global water accessibility monitoring \citep{ondaGlobalAccessSafe2012, jiaHighResolutionSpatialDistribution2016}. However, in an era of rapidly changing advanced technologies, international, and government policies, some of the older research might not be adequate for up to date information for  example of The eight Millennium Development Goals (MDGs) upgrading into The Sustainable Development Goals (SDGs). In light of the newest SDGs of providing clean and accessible drinking water for all by 2030, researchers have devoted their study to understand water accessibility in global and specific country levels.

%  Several empirical studies have focused on Facebook usage in adolescent girls (Tiggermann & Slater, 2013; Meier & Gray, 2014) and in young adult women (Smith, Hames, & Joiner, 2013; Fardouly et al., 2015; Cohen, Newton-John & Slater, 2017), while a systematic review by Holland and Timmerman (2016) confirmed a relationship between social networking and body image for both women and men. Across these studies, there is consistent evidence that body image issues are influenced not by social media usage in general, but by engagement with the visual and interactive aspects of these platforms.

>>>>

@@

\section{Contribution}
Lack of water accessibility is a major crisis for many vulnerable people around the world. We have determined to seek literature reviews from the past 15 years to have the most up to date information because information on water accessibility is a topic that is constantly changing throughout the world due to different international, government, and even local policies. The literature review intends to investigate different journal articles on water accessibility in a global scale. Therefore we can conduct a research to fill many major gaps  to analyze the water accessibility predictor variables which could increase and enhance water accessibility in global scale. We will always gain new insight and wisdom on information about water accessibility through the global scale as we investigate and determine literature reviews chronologically. 
\subsection{2006-2016}
Improving water accessibility have been a priority by many organizations around the world, realizing it is the basic human rights to have clean and accessible drinkable water in past 15 years. During 2006 to 2016, overall water accessibility has been improving by utilizing the indicators of the past \citep{fullerTrackingProgressGlobal2016}. However, some researchers raises concerns on lack of clarity with the global water accessibility monitoring \citep{ondaGlobalAccessSafe2012, jiaHighResolutionSpatialDistribution2016}. However, in an era of rapidly changing advanced technologies, international, and government policies, some of the older research might not be adequate for up to date information for  example of The eight Millennium Development Goals (MDGs) upgrading into The Sustainable Development Goals (SDGs). In light of the newest SDGs of providing clean and accessible drinking water for all by 2030, researchers have devoted their study to understand water accessibility in global and specific country levels. Several research and studies have focused global water accessibility ,and its progress \citep{sorensonSafeAccessSafe2011,bainAccountingWaterQuality2012,wssccWaterSanitationHygiene2014,  ondaGlobalAccessSafe2012, bartramGlobalMonitoringWater2014, ondaCountryClusteringApplied2014, whoDrinkingwater,fullerTrackingProgressGlobal2016, weiyuyuGlobalPerspectiveDrinkingwater2016, grahamAnalysisWaterCollection2016,overboOnplotDrinkingWater2016}. While there has been studies focusing on local community in different parts of the country learning about their water accessibility and sanitation initiation \citep{jagalsDoesImprovedAccess2006, geereDomesticWaterCarrying2010, simaWaterFlowsEnergy2013, hoChallengeGlobalWater2014, sakisakaIntroductionCommunityWater2015, jiaHighResolutionSpatialDistribution2016}. Where majority raised concerns about lack of monitoring sustainable water accessibility measurements for many people, and even few argues for greater focus in many people's access to drinking water sources. Nonetheless, there is a lack of robust study on modes of transportation related to enhance water accessibility for all people by 2030.
